Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-07-19 manuscript.Rmd
CAGR analysis

>>>>

```{r CAGR comparison}

CAGR <- function(start, finish, periods){
  # Function to compute the CAGR given simple returns
  #
  # args:
  #  start = starting value
  #  finish = ending cumulative value
  #  periods = number of time periods over which value was accumulated
  #
  # Returns the Compound Annual Growth Rate
    cagr <- round(((finish/start)^(1 /periods) - 1)*100, digits=2)    
  return(cagr)
}

setwd("C:/Users/beperron/Git/SocialWorkResearch/Data")
sangam <- read.csv("sangam.csv")

sangam.cumsum <-sangam %>%
  group_by(field) %>%
  mutate(CumSum=cumsum(count))

cagr <- sangam.cumsum %>%
  filter(year==1989 | year==1998)%>%
  group_by(field)%>%
  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9)) %>%
  select(field, cagr)

cagr<-unique(cagr)

############## Generate comparable social work CAGR, 1989-1998 #################

sw.cagr <- articles.df %>%
  filter(Year<1999 & Year>1988)%>%
  mutate(CumSum=cumsum(N)) %>%
  mutate(field = "socialWork")

sw.cagr <- sw.cagr %>%
  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9))%>%
  select(field, cagr)

sw.cagr<-unique(sw.cagr)

cagr<-rbind(cagr, sw.cagr)

cagr$field<-as.character(cagr$field)
cagr$field<-reorder(cagr$field, cagr$cagr)

#############PLOT##################

plot.cagr.ss <- ggplot(cagr, aes(x=field, y=cagr, fill=field, group =1)) + 
  theme_bw() + 
  geom_bar(width=0.8, stat='identity') +
  theme(axis.text.x = element_text(size=8), 
        title = element_text(size = 10), plot.title=element_text(size=10)) + 
  xlab("Field") + 
  ylab("Cumulative annual growth rate (%)") + 
  ggtitle("Cumulative annual growth rates for article production across the social sciences, 1989-1998") +
  theme(plot.title = element_text(size = rel(1.5))) +
  scale_y_continuous(breaks = c(seq(0, 40, 5)), limits=c(0, 40)) +
  theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))+
  scale_fill_manual(values=c("#b2abd2", "#b2abd2", "#fdb863", "#b2abd2", "#b2abd2", "#b2abd2", "#b2abd2"))+
  theme(legend.position="none") +
  scale_x_discrete(labels=c("Psychology","Economics","Social Work","Sociology","Political Science", "History", "Anthropology")) +
  geom_hline(yintercept=seq(0, 40, 15), col="white", lwd=0.6) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())

plot.cagr.ss
